### 2017-07-12 README.Rmd
implement diff in prop

```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = c("1" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop") #
```

Two categorical (2 level) variables (not yet implemented)

```
mtcars %>%
  select(am, vs) %>%
  hypothesize(null = "independence") %>% # 
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in props") #
```

>>>>

```
mtcars %>%
  select(am) %>%
  hypothesize(null = "point", p = c("1" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop")
```

Two categorical (2 level) variables

```
mtcars %>%
  select(am, vs) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in props")
```
